### 2015-03-12 intro.tex
Getting under 6,000 words
Spurious comma

We experimentally analyze the accuracy of the \zplus qualitative
probability scheme when used for diagnosis and information fusion.
In cyber defense, an ``intrusion detection system (IDS) is a device or
software application that monitors network or system activities for malicious
activities or policy violations''~\cite{wiki:ids}.
In previous work we developed a technique for IDS
fusion, deployed in the Scyllarus system~\anoncite{goldman:09Scyllarus}, and its
successor MIFD~\anoncite{stratus:saso12}.
These systems fuse together reports from multiple, heterogeneous IDSes,
hypothesizing underlying events to explain those reports, and assessing the events'
likelihood, to detect cyber attacks.
Their likelihood assessment is based on \zplus, a qualitative
abstraction of probability theory~\cite{Goldszmidt:96}.
Scyllarus has been extensively tested in real networks, using both
real and synthetic data, and has shown its ability to accurately fuse reports
from extremely noisy sensors. 
We also
drastically reduce false alarm rates, the bane of intrusion
detection systems, reducing the flood of incoming reports by multiple
orders of magnitude.
Unfortunately, it is difficult to draw crisp, \emph{general} conclusions based on
field evaluations alone.
We need to demonstrate that the results are due to features of the algorithm,
not simply artifacts of details of the test network, traffic, and
attacks.  This problem is particularly acute in the area of intrusion detection,
as we explain below.
% This is a general problem of evaluating IDSes, which we discuss
% further below.
%

@@

In the next section we introduce the problem of \ids fusion
and its challenges.  Then we describe our approach to the
problem, as implemented in the Scyllarus and MIFD systems.  We describe our
experimental designs, present the results and conclude with some proposals for
future work.

>>>>

We experimentally analyze the accuracy of the \zplus qualitative
probability scheme when used for diagnosis and information fusion.
In cyber defense, an ``intrusion detection system (IDS) is a device or
software application that monitors network or system activities for malicious
activities or policy violations''~\cite{wiki:ids}.
In previous work we developed a technique for IDS
fusion, deployed in the Scyllarus system~\anoncite{goldman:09Scyllarus} and its
successor MIFD~\anoncite{stratus:saso12}.
These systems fuse together reports from multiple, heterogeneous IDSes,
hypothesizing underlying events to explain those reports, and assessing the events'
likelihood, to detect cyber attacks.
Their likelihood assessment is based on \zplus, a qualitative
abstraction of probability theory~\cite{Goldszmidt:96}.
Scyllarus has been extensively tested in real networks, using both
real and synthetic data, and has shown its ability to accurately fuse reports
from extremely noisy sensors. 
We also
drastically reduce false alarm rates, the bane of intrusion
detection systems, reducing the flood of incoming reports by multiple
orders of magnitude.
Unfortunately, it is difficult to draw crisp, \emph{general} conclusions based on
field evaluations alone.
We need to demonstrate that the results are due to features of the algorithm,
not simply artifacts of details of the test network, traffic, and
attacks.  This problem is particularly acute in the area of intrusion detection,
as we explain below.
% This is a general problem of evaluating IDSes, which we discuss
% further below.
%

@@

In the next section we introduce the problem of \ids fusion
and its challenges.  Then we describe our approach to the
problem, as implemented in the Scyllarus and MIFD systems.  We describe our
experimental designs, present the results, and conclude with some proposals for
future work.
